A Partitioning Algorithm for Maximum Common Subgraph Problems

### 2017-02-17 paper/paper.tex
Do or do not, there is no try
Open conclude

We have introduced the \McSplit\ algorithm for Max Common Subgraph.  The new
algorithm is more than an order of magnitude faster than the previous state of
the art for unlabelled and undirected instances. We have shown how the
algorithm can be extended for graphs with labels on edges, labels on vertices,
loops, directed edges and the requirement that the resultant graph be
connected.

To further improve the state of the art, we could try creating a hybrid
algorithm.  This could use $k{\downarrow}$ initially, switching to \McSplit\ when
the extra filtering is ineffective, and finally switching to a clique encoding
when fewer than some threshold number of vertices remain to be selected. This
might deliver the benefits of the clique encoding for labelled graphs, while
avoiding the high memory cost and colouring time of encoding the full instance.

>>>>

We have introduced the \McSplit\ algorithm for maximum common subgraph
problems.  This algorithm is more than an order of magnitude faster than the
previous state of the art for unlabelled and undirected instances. We have
shown how the algorithm can be extended for graphs with labels on edges, labels
on vertices, loops, directed edges and the requirement that the resultant graph
be connected.

To further improve the state of the art, we could create a hybrid
algorithm.  This could use $k{\downarrow}$ initially, switching to \McSplit\ when
the extra filtering is ineffective, and finally switching to a clique encoding
when fewer than some threshold number of vertices remain to be selected. This
might deliver the benefits of the clique encoding for labelled graphs, while
avoiding the high memory cost and colouring time of encoding the full instance.
